plyranges: a grammar for transforming genomics data

### 2018-05-16 README.Rmd
- more detail in readme

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(tibble)
library(knitr)
library(ggbio)
library(plyranges)
library(stringr)
library(dplyr)
library(readr)
library(Biostrings)
library(AnnotationHub)
```
# plyranges-paper
The setup chunk in the [paper](paper.Rmd) shows how to download the data with R.

Requires the following packages (and versions) to reproduce the paper:

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(tibble)
library(knitr)
library(ggbio)
library(plyranges)
library(stringr)
library(dplyr)
library(readr)
library(Biostrings)
library(AnnotationHub)
```
# plyranges-paper

The setup chunk in the [paper](paper.Rmd) shows how to download the data with R.

The paper uses the current development version of `plyranges` which
you can install from github using:

```{r, eval = FALSE}
source("https://bioconductor.org/biocLite.R")
biocLite("sa-lee/plyranges")
```

The following packages (and versions) are required to reproduce the paper:
